### 2019-06-09 doc/chapters/challenge_stainless.tex
text
changed text

In this chapter we explore the practical challenges that could occur by using Stainless.

@@

Invoking the JAR on our source code Stainless will verify it.
If we have a bigger project, this becomes really tricky because we must pass all files needed including the dependencies.
This is in contrast to the sbt plugin, where we can integrate Stainless in our compilation process.
When we call compile, Stainless verifies the code and stops the compilation if the verification fails.

@@

Now we can finally run Stainless on our code.
But this leads us to the next findings described in the previous chapters.

>>>>

In this chapter we look at the practical challenges that could occur by using Stainless.
Since Stainless is still in development and there is no 1.x release there might still be breaking changes and improvements fixing problems discribed now.

@@

Invoking the JAR on our source code Stainless will verify it.
If we have a bigger project, this becomes really tricky, because we must pass all files needed including the dependencies.
This is in contrast to the sbt plugin, where we can integrate Stainless in our compilation process.
When we call compile, Stainless verifies the code and stops the compilation if the verification fails.

@@

Now we can finally run Stainless on our code.
But this leads us to the next findings.
We must rewrite most of the code, as described in the previous chapters.
